---
title: Playground
author: M. Megahed
subtitle: Statistical Programming Languages - SoSe 2019
output:
  html_document: 
    toc: true
    toc_float:
        collapsed: false
        smooth_scroll: false
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
# will knit with errors (to change: errors = TRUE)
# will knit without results, to show: results = 'show'
solution <- FALSE
if(solution == FALSE){
knitr::opts_chunk$set(error = TRUE, echo = FALSE, results = 'show', message = FALSE, warning = FALSE, fig.keep = 'none', cache = FALSE)
}
options(repos=c(CRAN = "https://cran.uni-muenster.de/"))
```

<!-- 
  YAML stuff
  
  HTML Properties:
  https://bookdown.org/yihui/rmarkdown/html-document.html 

  PDF and LaTeX
  https://bookdown.org/yihui/rmarkdown/pdf-document.html
  
  date: '`r format(Sys.time(), ''%d %B, %Y'')`'

-->



## R Markdown

This is an R \alpha Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
